The Galaxy Cluster Merger Catalog: An Online Repository of Mock Observations from Simulated Galaxy Cluster Mergers

### 2017-04-05 paper/ms.tex
Add keywords to paper
Updates to the paper for referee response

\author{J. A. ZuHone\altaffilmark{1}, K. Kowalik\altaffilmark{2}}

\altaffiltext{1}{Harvard-Smithsonian Center for Astrophysics, 60 Garden St., Cambridge, MA 02138, USA}
\altaffiltext{2}{National Center for Supercomputing Applications, University of Illinois at Urbana-Champaign, 1205 W. Clark St., MC-257, Urbana, IL 61801, USA}

@@

@@

At the time of writing, the catalog contains data products from idealized binary cluster merger
simulations. In the future, the catalog will include data products from a variety of galaxy cluster merger and related galaxy cluster simulations, including those from cosmological simulations and simulations of interactions between clusters and their member galaxies. The types of data products are likely to expand and diversify with the inclusion of new simulations.

@@

\subsubsection{The yt Hub}\label{sec:yt_hub}
The catalog data is stored on the \code{yt Hub}\footnote{\url{https://hub.yt/}}, a conglomerate of various open source
services creating an environment that allows one to collect, remotely analyze, share and publish scientific datasets. At
its core, the \code{yt Hub} uses \code{Girder}\footnote{\url{https://girder.readthedocs.io}}, a data management platform
that allows to transparently store, serve, and proxy data from heterogeneous backend storage engines through a single
web API. Data served by \code{Girder} can easily be gathered into dynamical hierarchies such as collections, folders and
items.  This data management system is integrated with
\code{JupyterHub}\footnote{\url{https://jupyterhub.readthedocs.io/}} and allows authenticated users to spawn Jupyter
notebook servers with direct access to the data that is provided as a dynamically composed FUSE filesystem. Any Jupyter
notebook created in that environment during an interactive session is safely stored back in the \code{Girder} instance,
preserving the user's analysis workflow and increasing research reproducibility. In the future, we plan to have this
notebook capability integrated directly with the catalog website.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{set_page.png}
\caption{An example ``set page''. Links are provided to original journal articles, various simulation parameters and other information are tabulated, and links to the data for the individual simulations appear here. This particular page is linked at \url{http://gcmc.hub.yt/virgo/index.html}.}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{sim_page.png}
\caption{An example ``simulation page''. Slider bars allow exploration of different epochs, and buttons near the top choose different projection axes. The figures link to the page for the files for the corresponding epoch of the simulation. This particular page is linked at \url{http://gcmc.hub.yt/virgo/novisc/index.html}.}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{epoch_page.png}
\caption{An example ``epoch page''. Links are provided to similar simulations with different physics at the same epoch at the top of the page. For each data type, figures of some of the fields are shown and links to download the data or display in JS9 are provided. This particular page is linked at \url{http://gcmc.hub.yt/virgo/novisc/0046.html}.}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{epoch_page2.png}
\caption{The bottom of an ``epoch page'', showing the simulated X-ray event file, the link to the Jupyter notebook directions, and the JS9 interface with a projection file loaded, and a circular region selected. This particular page is linked at \url{http://gcmc.hub.yt/virgo/novisc/0046.html}.}
\end{center}
\end{figure*}

@@

@@

The web interface to the catalog is designed to provide straightforward interactive browsing of a given simulation's data across its many epochs and between several projection axes. This facilitates comparisons between the mock observations and actual observations of clusters so that a potential analog of a particular system may be found easily.

@@

@@

@@

\begin{thebibliography}{}
\bibitem[Astropy Collaboration et al.(2013)]{apy13} Astropy Collaboration, Robitaille, T.~P., Tollerud, E.~J., et al.\ 2013, \aap, 558, A33
\bibitem[Berger \& Colella(1989)]{ber89} Berger, M.~J., \& Colella, P.\ 1989, Journal of Computational Physics, 82, 64
\bibitem[Br{\"u}ggen et al.(2012)]{bru12} Br{\"u}ggen, M., Bykov, A., Ryu, D., R{\"o}ttgering, H.\ 2012, \ssr, 166, 187
\bibitem[Brunetti \& Lazarian(2007)]{bru07} Brunetti, G., \& Lazarian, A.\ 2007, \mnras, 378, 245
\bibitem[Colella \& Woodward(1984)]{col84} Colella, P., \& Woodward, P.~R.\ 1984, Journal of Computational Physics, 54, 174
\bibitem[Greisen \& Calabretta(2002)]{gre02} Greisen, E.~W., \& Calabretta, M.~R.\ 2002, \aap, 395, 1061
\bibitem[Calabretta \& Greisen(2002)]{cal02} Calabretta, M.~R., \& Greisen, E.~W.\ 2002, \aap, 395, 1077
\bibitem[Clowe et al.(2004)]{clo04} Clowe, D., Gonzalez, A., \& Markevitch, M.\ 2004, \apj, 604, 596
\bibitem[Chluba et al.(2012)]{chl12} Chluba, J., Nagai, D., Sazonov, S., \& Nelson, K.\ 2012, \mnras, 426, 510
\bibitem[Chluba et al.(2013)]{chl13} Chluba, J., Switzer, E., Nelson, K., \& Nagai, D.\ 2013, \mnras, 430, 3054
\bibitem[Donnert et al.(2013)]{don13} Donnert, J., Dolag, K., Brunetti, G., \& Cassano, R.\ 2013, \mnras, 429, 3564
\bibitem[{Dubey} et~al.(2009)]{dub09} {Dubey}, A., {Antypas}, K.,
  {Ganapathy}, M.~K., {Reid}, L.~B., {Riley}, K.~M., {Sheeler}, D.,
  {Siegel}, A., {Weide}, K. Extensible component based architecture
  for FLASH, a massively parallel, multiphysics simulation
  code. Parallel Computing 35~(10-11), 512--522.
\bibitem[Evans \& Hawley(1988)]{eva88} Evans, C.~R., \& Hawley, J.~F.\ 1988, \apj, 332, 659
\bibitem[Feretti(2005)]{fer05} Feretti, L.\ 2005, Advances in Space Research, 36, 729
\bibitem[Ford et al.(2014)]{for14} Ford, J., Hildebrandt, H., Van Waerbeke, L., et al.\ 2014, \mnras, 439, 3755
\bibitem[Forman et al.(1972)]{for72} Forman, W., Kellogg, E., Gursky, H., Tananbaum, H., \& Giacconi, R.\ 1972, \apj, 178, 309
\bibitem[Markevitch et al.(2004)]{mar04} Markevitch, M., Gonzalez, A.~H., Clowe, D., et al.\ 2004, \apj, 606, 819
\bibitem[Pence et al.(2010)]{pen10} Pence, W.~D., Chiappetti, L., Page, C.~G., Shaw, R.~A., \& Stobie, E.\ 2010, \aap, 524, A42
\bibitem[Poole et al.(2006)]{poo06} Poole, G.~B., Fardal, M.~A., Babul, A., McCarthy, I.~G., Quinn, T., \& Wadsley, J.\ 2006, \mnras, 373, 881
\bibitem[Ricker \& Sarazin(2001)]{ric01} Ricker, P.~M., \& Sarazin, C.~L.\ 2001, \apj, 561, 621
\bibitem[Ricker(2008)]{ric08} Ricker, P.~M.\ 2008, \apjs, 176, 293-300
\bibitem[Skillman et al.(2013)]{ski13} Skillman, S.~W., Xu, H., Hallman, E.~J., et al.\ 2013, \apj, 765, 21
\bibitem[Stone et al.(2008)]{sto08} Stone, J.~M., Gardiner, T.~A., Teuben, P., Hawley, J.~F., \& Simon, J.~B.\ 2008, \apjs, 178, 137
\bibitem[Sunyaev \& Zeldovich(1972)]{sun72} Sunyaev, R.~A., \& Zeldovich, Y.~B.\ 1972, Comments on Astrophysics and Space Physics, 4, 173
\bibitem[Turk et al.(2011)]{tur11} Turk, M.~J., Smith, B.~D., Oishi, J.~S., Skory, S., Skillman, S.~W., Abel, T., \& Norman, M.~L.\ 2011, \apjs, 192, 9
\bibitem[van Weeren et al.(2010)]{vwe10} van Weeren, R.~J., R{\"o}ttgering, H.~J.~A., Br{\"u}ggen, M., \& Hoeft, M.\ 2010, Science, 330, 347
\bibitem[Vazza et al.(2009)]{vaz09} Vazza, F., Brunetti, G., Kritsuk, A., et al.\ 2009, \aap, 504, 33
\bibitem[Yu et al.(2015)]{yu15} Yu, L., Nelson, K., \& Nagai, D.\ 2015, \apj, 807, 12
\bibitem[ZuHone et al.(2010)]{zuh10} ZuHone, J.~A., Markevitch, M., \& Johnson, R.~E.\ 2010, \apj, 717, 908 (ZMJ10)
\bibitem[ZuHone(2011)]{zuh11} ZuHone, J.~A.\ 2011, \apj, 728, 54 (Z11)
\bibitem[ZuHone et al.(2014)]{zuh14} ZuHone, J.~A., Biffi, V., Hallman, E.~J., et al.\ 2014, arXiv:1407.1783
\bibitem[Zwicky(1937)]{zwi37} Zwicky, F.\ 1937, \apj, 86, 217
\end{thebibliography}{}

>>>>

\author{J. A. ZuHone\altaffilmark{1}, K. Kowalik\altaffilmark{2}, E. \"{O}hman\altaffilmark{3}, E. Lau\altaffilmark{3}}

\altaffiltext{1}{Harvard-Smithsonian Center for Astrophysics, 60 Garden St., Cambridge, MA 02138, USA}
\altaffiltext{2}{National Center for Supercomputing Applications, University of Illinois at Urbana-Champaign, 1205 W. Clark St., MC-257, Urbana, IL 61801, USA}
\altaffiltext{3}{Department of Physics, Yale University, New Haven, CT 06520, USA}

@@

\keywords{galaxies: clusters: general --- catalogs --- methods: hydrodynamic simulations}

@@

At the time of writing, the catalog contains data products from idealized binary cluster merger
simulations. {\bf The original works from which these simulations are drawn, in addition to some details of the simulations, are listed in Table \ref{tab:sim_table}.} The types of data products listed here are appropriate for such simulations. In the future, the catalog will include data products from a variety of cluster merger and related simulations, including those from cosmological simulations and simulations of interactions between clusters and their member galaxies. The types of data products are likely to expand and diversify with the inclusion of new simulations. \textbf{For more discussion of future directions for the catalog and long-term issues, see Section \ref{sec:future}}.

\input{tab1.tex}

@@

\subsubsection{The yt Hub}\label{sec:yt_hub}
The catalog data is stored on the \code{yt Hub}\footnote{\url{https://hub.yt/}}, a conglomerate of various open source
services \textbf{hosted at the National Center for Supercomputing Applications (NCSA)}, creating an environment that allows one to collect, remotely analyze, share and publish scientific datasets. At its core, the \code{yt Hub} uses \code{Girder}\footnote{\url{https://girder.readthedocs.io}}, a data management platform that allows to transparently store, serve, and proxy data from heterogeneous backend storage engines through a single
web API. Data served by \code{Girder} can easily be gathered into dynamical hierarchies such as collections, folders and
items. This data management system is integrated with \code{JupyterHub}\footnote{\url{https://jupyterhub.readthedocs.io/}} and allows authenticated users to spawn Jupyter notebook servers with direct access to the data that is provided as a dynamically composed FUSE filesystem. Any Jupyter
notebook created in that environment during an interactive session is safely stored back in the \code{Girder} instance,
preserving the user's analysis workflow and increasing research reproducibility. In the future, we plan to have this
notebook capability integrated directly with the catalog website.

@@

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{set_page.eps}
\caption{An example ``set page''. Links are provided to original journal articles, various simulation parameters and other information are tabulated, and links to the data for the individual simulations appear here. This particular page is linked at \url{http://gcmc.hub.yt/virgo/index.html}.}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{sim_page.eps}
\caption{An example ``simulation page''. Slider bars allow exploration of different epochs, and buttons near the top choose different projection axes. The figures link to the page for the files for the corresponding epoch of the simulation. This particular page is linked at \url{http://gcmc.hub.yt/virgo/novisc/index.html}.}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{epoch_page.eps}
\caption{An example ``epoch page''. Links are provided to similar simulations with different physics at the same epoch at the top of the page. For each data type, figures of some of the fields are shown and links to download the data or display in JS9 are provided. This particular page is linked at \url{http://gcmc.hub.yt/virgo/novisc/0046.html}.}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{epoch_page2.eps}
\caption{The bottom of an ``epoch page'', showing the simulated X-ray event file, the link to the Jupyter notebook directions, and the JS9 interface with a projection file loaded, and a circular region selected. This particular page is linked at \url{http://gcmc.hub.yt/virgo/novisc/0046.html}.}
\end{center}
\end{figure*}

@@

The web interface to the catalog is designed to provide straightforward interactive browsing of a given simulation's data across its many epochs and between several projection axes. This facilitates comparisons between the mock observations and actual observations of clusters so that a potential analog of a particular system may be found easily. \textbf{Like the data itself, the web interface is also hosted at NCSA.}

@@

\section{Future Directions}\label{sec:future}

{\bf There are a number of extensions to the catalog and its capabilities that we envision for the future, which we briefly discuss in this section.}

\subsection{Adding New Simulations}\label{sec:new_sims}

{\bf The catalog is designed to be easily expanded to include new simulation data products related to galaxy cluster mergers or the more general arena of galaxy clusters, groups, or galaxies in the cosmological context. Indeed, work is already underway to incorporate simulated clusters from a cosmological simulation into the catalog, from the simulations of \citet{nel14}. The presentation of these clusters will necessarily be somewhat different from the binary merger simulations, since there are a much larger number of clusters in the cosmological volume, and each of these have evolved over time. For this reason, the pages associated with this simulation data will be divided up by cluster ID as well as epoch.

One way to encourage the inclusion of new simulations in the catalog is to provide Python scripts which may be used to generate the data products, including FITS image and table files and PNG images. A future version of the catalog will include a suite of such scripts which will be publicly available for this purpose, and directions for how to upload the resultant products to the \code{yt Hub}.}

\subsection{Adding New Data Products}\label{sec:new_data}

{\bf The current data products include slices and projections of various physical quantities, but they have a distinct tilt towards X-ray observations of clusters due to the focus of the simulations included so far on the physics of the ICM. Many other simulations of clusters available in the literature have additional physics included in the simulation, such as star formation, active galactic nuclei, and relativistic particle acceleration. These physical processes produce observations in other wavebands, such as the optical, ultraviolet, or radio, which could be included as simulated observations in the form of new FITS image or table types in the catalog.}

\subsection{Sustainability}\label{sec:sustainability}

{\bf Maintaining such a large catalog of data, whether from simulations or otherwise, is a substantial undertaking. It first and foremost requires that the computational resources necessary to store the data and serve it to users will be maintained and funded for the forseeable future. The website \url{http://gcmc.hub.yt} itself (including the widgets, documentation, and user interface) is completely separated from the data itself, which is hosted on the yt Hub. Therefore it is completely portable, and may be hosted virtually anywhere, provided proper configuration of Cross-Origin Resource Sharing (CORS) between it and the \code{yt Hub}.

As for the \code{yt Hub} itself, its infrastructure and software is an integral part of other NCSA projects related to data publication and data provenance\footnote{One such example being WholeTale, \url{https://www.nsf.gov/awardsearch/showAward?AWD_ID=1541450}}, which we hope makes it sustainable for the foreseeable future.

The second important resource is of course that of the human beings who are maintaining and updating the catalog. The authors themselves are committed to the long-term development and maintenance of the various components required to sustain this project, and our hope is that by getting more researches involved by including their data we can make the catalog a project which is sustained by a wider community. As a first step toward this goal, the code for the website is open-source and hosted at \url{http://github.com/jzuhone/cluster_merger_catalog}. Next steps include streamlining the code for the website itself and providing templates to simplify the generation of pages for new simulations, including directions for how to create a new set of pages for a simulation and how to submit them as a pull request to the repository.}

@@

\textbf{This initial release includes data products from binary merger simulations carried out by the first author, but the catalog is released and designed with the intent that it may be expanded to include simulation data products related to galaxy cluster mergers or the broader subject of cosmological structure formation from other works and authors. We have already received a positive response from the community in this regard and have plans underway to incorporate new simulations into the catalog in the near future.}

@@

\begin{thebibliography}{}
\bibitem[Astropy Collaboration et al.(2013)]{apy13} Astropy Collaboration, Robitaille, T.~P., Tollerud, E.~J., et al.\ 2013, \aap, 558, A33
\bibitem[Berger \& Colella(1989)]{ber89} Berger, M.~J., \& Colella, P.\ 1989, Journal of Computational Physics, 82, 64
\bibitem[Br{\"u}ggen et al.(2012)]{bru12} Br{\"u}ggen, M., Bykov, A., Ryu, D., R{\"o}ttgering, H.\ 2012, \ssr, 166, 187
\bibitem[Brunetti \& Lazarian(2007)]{bru07} Brunetti, G., \& Lazarian, A.\ 2007, \mnras, 378, 245
\bibitem[Colella \& Woodward(1984)]{col84} Colella, P., \& Woodward, P.~R.\ 1984, Journal of Computational Physics, 54, 174
\bibitem[Greisen \& Calabretta(2002)]{gre02} Greisen, E.~W., \& Calabretta, M.~R.\ 2002, \aap, 395, 1061
\bibitem[Calabretta \& Greisen(2002)]{cal02} Calabretta, M.~R., \& Greisen, E.~W.\ 2002, \aap, 395, 1077
\bibitem[Clowe et al.(2004)]{clo04} Clowe, D., Gonzalez, A., \& Markevitch, M.\ 2004, \apj, 604, 596
\bibitem[Chluba et al.(2012)]{chl12} Chluba, J., Nagai, D., Sazonov, S., \& Nelson, K.\ 2012, \mnras, 426, 510
\bibitem[Chluba et al.(2013)]{chl13} Chluba, J., Switzer, E., Nelson, K., \& Nagai, D.\ 2013, \mnras, 430, 3054
\bibitem[Donnert et al.(2013)]{don13} Donnert, J., Dolag, K., Brunetti, G., \& Cassano, R.\ 2013, \mnras, 429, 3564
\bibitem[{Dubey} et~al.(2009)]{dub09} {Dubey}, A., {Antypas}, K.,
  {Ganapathy}, M.~K., {Reid}, L.~B., {Riley}, K.~M., {Sheeler}, D.,
  {Siegel}, A., {Weide}, K. Extensible component based architecture
  for FLASH, a massively parallel, multiphysics simulation
  code. Parallel Computing 35~(10-11), 512--522.
\bibitem[Evans \& Hawley(1988)]{eva88} Evans, C.~R., \& Hawley, J.~F.\ 1988, \apj, 332, 659
\bibitem[Feretti(2005)]{fer05} Feretti, L.\ 2005, Advances in Space Research, 36, 729
\bibitem[Ford et al.(2014)]{for14} Ford, J., Hildebrandt, H., Van Waerbeke, L., et al.\ 2014, \mnras, 439, 3755
\bibitem[Forman et al.(1972)]{for72} Forman, W., Kellogg, E., Gursky, H., Tananbaum, H., \& Giacconi, R.\ 1972, \apj, 178, 309
\bibitem[Markevitch et al.(2004)]{mar04} Markevitch, M., Gonzalez, A.~H., Clowe, D., et al.\ 2004, \apj, 606, 819
\bibitem[Nelson et al.(2014)]{nel14} Nelson, K., Lau, E.~T., Nagai, D., Rudd, D.~H., \& Yu, L.\ 2014, \apj, 782, 107 
\bibitem[Pence et al.(2010)]{pen10} Pence, W.~D., Chiappetti, L., Page, C.~G., Shaw, R.~A., \& Stobie, E.\ 2010, \aap, 524, A42
\bibitem[Poole et al.(2006)]{poo06} Poole, G.~B., Fardal, M.~A., Babul, A., McCarthy, I.~G., Quinn, T., \& Wadsley, J.\ 2006, \mnras, 373, 881
\bibitem[Ricker \& Sarazin(2001)]{ric01} Ricker, P.~M., \& Sarazin, C.~L.\ 2001, \apj, 561, 621
\bibitem[Ricker(2008)]{ric08} Ricker, P.~M.\ 2008, \apjs, 176, 293-300
\bibitem[Skillman et al.(2013)]{ski13} Skillman, S.~W., Xu, H., Hallman, E.~J., et al.\ 2013, \apj, 765, 21
\bibitem[Stone et al.(2008)]{sto08} Stone, J.~M., Gardiner, T.~A., Teuben, P., Hawley, J.~F., \& Simon, J.~B.\ 2008, \apjs, 178, 137
\bibitem[Sunyaev \& Zeldovich(1972)]{sun72} Sunyaev, R.~A., \& Zeldovich, Y.~B.\ 1972, Comments on Astrophysics and Space Physics, 4, 173
\bibitem[Turk et al.(2011)]{tur11} Turk, M.~J., Smith, B.~D., Oishi, J.~S., Skory, S., Skillman, S.~W., Abel, T., \& Norman, M.~L.\ 2011, \apjs, 192, 9
\bibitem[van Weeren et al.(2010)]{vwe10} van Weeren, R.~J., R{\"o}ttgering, H.~J.~A., Br{\"u}ggen, M., \& Hoeft, M.\ 2010, Science, 330, 347
\bibitem[Vazza et al.(2009)]{vaz09} Vazza, F., Brunetti, G., Kritsuk, A., et al.\ 2009, \aap, 504, 33
\bibitem[Yu et al.(2015)]{yu15} Yu, L., Nelson, K., \& Nagai, D.\ 2015, \apj, 807, 12
\bibitem[ZuHone et al.(2010)]{zuh10} ZuHone, J.~A., Markevitch, M., \& Johnson, R.~E.\ 2010, \apj, 717, 908
\bibitem[ZuHone(2011)]{zuh11a} ZuHone, J.~A.\ 2011, \apj, 728, 54
\bibitem[ZuHone et al.(2011)]{zuh11b} ZuHone, J.~A., Markevitch, M., \& Lee, D.\ 2011, \apj, 743, 16
\bibitem[ZuHone et al.(2014)]{zuh14} ZuHone, J.~A., Biffi, V., Hallman, E.~J., et al.\ 2014, arXiv:1407.1783
\bibitem[ZuHone et al.(2015)]{zuh15} ZuHone, J.~A., Kunz, M.~W., Markevitch, M., Stone, J.~M., \& Biffi, V.\ 2015, \apj, 798, 90
\bibitem[Zwicky(1937)]{zwi37} Zwicky, F.\ 1937, \apj, 86, 217
\end{thebibliography}{}
